Applying the new names to the baseline

### 2024-07-02 extras/Applying-New-Names-To-Baseline/applying-new-names-to-baseline.Rmd
writing the loci-renamed baseline file.
(Also, I copied that to data)
Change sample column name to indiv

# and then we also want to add the rosa genotypes on there, AND remove the SacNonW fish
final <- wide_ordered_no_rosa %>%
  left_join(csv2 %>% select(Sample_ID, hapstr), by = join_by(Sample_ID)) %>%
  mutate(rosa_genotypes_str = hapstr, .after = sample_type) %>%
  select(-hapstr) %>%
  filter(!(collection == "SacNonW"))
```

@@

```{r}
dir.create("results", showWarnings = FALSE)
write_csv(final, "results/subRoSA_baseline_rubias_loci_renamed_July_2024.csv")
```

>>>>

# and then we also want to add the rosa genotypes on there, AND remove the SacNonW fish
final <- wide_ordered_no_rosa %>%
  left_join(csv2 %>% select(Sample_ID, hapstr), by = join_by(Sample_ID)) %>%
  mutate(rosa_genotypes_str = hapstr, .after = sample_type) %>%
  select(-hapstr) %>%
  filter(!(collection == "SacNonW")) %>%
  rename(indiv = Sample_ID)
```

@@

```{r}
dir.create("results", showWarnings = FALSE)
write_csv(final, "results/subRoSA_baseline_rubias_loci_renamed_July_2024.csv.gz")
```
